%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins for maximum page usage
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting (tightened vertical space)
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

% Tightened list spacing commands
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=1pt, parsep=0pt, topsep=1pt, partopsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-8pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Ahmad Al-Aloosi} \\ \vspace{1pt}
    \small 647-675-0725 $|$ \href{mailto:ahmad@aloosi.ca}{\underline{ahmad@aloosi.ca}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/aloosi}} $|$
    \href{https://github.com/...}{\underline{github.com/aloosi}}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\resumeItemListStart
\resumeItem{Computer science graduate with project-based backend experience in Go, SQL, and modern web stacks.}
\resumeItem{Built end-to-end systems involving REST APIs, relational data modeling, authentication, and admin tooling.}
\resumeItem{Professional background in data analytics, delivering automated KPI pipelines and high-usage dashboards.}
\resumeItemListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Toronto Metropolitan University}{Toronto, ON}
      {Bachelor of Science in Computer Science}{Sep. 2019 -- May 2025}
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Languages}{: Go, Python, SQL, JavaScript} \\
    \textbf{Backend}{: Gin, Flask, REST APIs, JWT, RBAC} \\
    \textbf{Data}{: PostgreSQL, Snowflake, Data Modeling} \\
    \textbf{Cloud \& DevOps}{: AWS (EC2, RDS, S3, Lambda), Docker, Kubernetes}
    }}
\end{itemize}
 
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Parental Leave}{Oct. 2025 -- Present}
      {}{}
      
    \resumeSubheading
      {Data Analytics Engineer}{Aug. 2023 -- Oct. 2025}
      {Signify Lighting}{Markham, ON}
      \resumeItemListStart
        \resumeItem{Automated KPI tracking for rebate disputes, improving resolution rates by \textbf{33\% QoQ} and reducing exposure tied to processing errors (estimated risk impact \textbf{\$615M}).}
        \resumeItem{Developed and maintained an enterprise \textbf{Order Intake Power BI dashboard} ranked in the \textbf{top 0.2\%} of organizational usage (13 of 6,505 reports).}
        \resumeItem{Optimized Snowflake queries and data models, reducing Power BI load times for N.A. sales dashboards by \textbf{45 minutes}.}
        \resumeItem{Designed and deployed cross-departmental KPI dashboards used by sales, supply chain, and finance teams.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Travel Agency Reservation System} $|$ \emph{Go, React, AWS}}{}
          \resumeItemListStart
            \resumeItem{Built a full-stack reservation system with a Go (Gin) backend and React frontend, supporting concurrent booking requests and real-time status updates.}
            \resumeItem{Implemented RESTful APIs and deployed the service on AWS EC2 with a Postgres-backed data layer.}
            \resumeItem{Added Redis-based caching using a cache-aside pattern, reducing repeated database queries and improving response times.}
            \resumeItem{Used k6 to load-test key endpoints and validate stable performance under simulated concurrent users.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{BrightPixel Online Service Store Platform} $|$ \emph{Go, Next.js, PostgreSQL}}{}
          \resumeItemListStart
            \resumeItem{Designed and built a \textbf{full-stack e-commerce platform} with a Go (Gin) backend and Next.js frontend, implementing \textbf{50+ RESTful API endpoints} across \textbf{8 core domains} including products, orders, payments, reviews, stores, delivery, and authentication.}
            \resumeItem{Architected a \textbf{PostgreSQL relational schema with 15+ tables}, supporting multi-store inventory management, order lifecycles, and transactional payment workflows.}
            \resumeItem{Implemented \textbf{JWT-based authentication and role-based access control (RBAC)}, securing admin-only endpoints and supporting concurrent user sessions.}
            \resumeItem{Built an \textbf{admin dashboard} for product catalog management, order fulfillment, payment processing with discount codes and gift cards, and review moderation across multiple store locations.}
            \resumeItem{Wrote \textbf{unit and integration tests using testify}, validating authentication flows and critical business logic to ensure API reliability.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Alexa Brown Noise Skill} $|$ \emph{Python, Alexa ASK SDK, AWS (Lambda, S3, Budgets)}}{}
          \resumeItemListStart
            \resumeItem{Engineered a voice-activated Alexa Skill using \textbf{Python} and the \textbf{ASK SDK} to provide high-fidelity brown noise streaming with integrated play/pause/resume functionality.}
            \resumeItem{Deployed a serverless backend on \textbf{AWS Lambda} to process custom intents and manage skill session states, maintaining a \textbf{sub-500ms execution latency}.}
            \resumeItem{Optimized audio delivery by hosting assets on \textbf{AWS S3}, ensuring high-availability and low-latency streaming for concurrent Alexa devices.}
            \resumeItem{Implemented proactive \textbf{AWS Budgeting and billing alarms} to monitor resource consumption, successfully maintaining \textbf{100\% cost-efficiency} within the Free Tier thresholds.}
            \resumeItem{Managed end-to-end integration between the Amazon Developer Console and Lambda APIs, including secure IAM role configuration and endpoint validation.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}